Manuscript1_figures

### 2025-05-06 Manuscript1_figures.Rmd
Revising scripts to include all figures

Includes figures 6-9, S1, S3, and S4
```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(pacman)
pacman::p_load(tidyverse, readxl, stringr, readr, glmnet, ISLR, lubridate, ggplot2, ggpubr, stats, gridExtra, graphics, gt)
```

@@

BVRDO2 <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/725/5/b7f0524aee78dcf4a2452a203a39c1f2")
```

```{r}
#set up file path for figures, change if necessary
myFilePath <- './figures'
```

## Seasonal Flux Paired T-Test Plot (Figure 6)

```{r Fig 6 and 7 set up, eval=TRUE, include=FALSE}
 fluxes2018_2023 <-  fluxes %>% 
  select(Reservoir, Date, Depth_m, Duration_days, TFeFlux_gm2d, TMnFlux_gm2d) %>% 
  na.omit() %>%
  mutate(Layer = if_else(Depth_m <= 5, 'Epilimnion', 'Hypolimnion'),
         Year = year(Date))

@@

```{r Figure 6 script, eval=TRUE, include=FALSE}
CumulFePlot1 <- CumulFluxSummary %>% 
  ggplot() + theme_bw(base_size = 18) + ggtitle('Iron') + ylab('Fe Flux (g/m2d)') +
  geom_point(aes(x = Reservoir, y = FeFlux, color = as.factor(Year), shape = as.factor(Year)), size = 3) +
  #2018
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.209, yend = 1.196, alpha = 0.5,
               color = "#F8766D", linetype = 3) +
  #2019
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.661, yend = 1.398, alpha = 0.5,
               color = "#B79F00", linetype = 3) +
  #2020
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.276, yend = 1.676, alpha = 0.5,
               color = "#00BA38", linetype = 3) +
  #2021
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.775, yend = 1.776, alpha = 0.5,
               color = "#00BFC4", linetype = 3) +
  #2022
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.867, yend = 1.849, alpha = 0.5,
               color = "#619CFF", linetype = 3) +
  #2023
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.819, yend = 1.017, alpha = 0.5,
               color = "#F564E3", linetype = 3) +
  annotate(geom = 'text', x= 1.5, y = 1.8, label = '**', size = 12) +
  guides(color = guide_legend(title = 'Year'), shape = guide_legend(title = 'Year'))

@@

```{r Figure 6, eval=TRUE, include=TRUE}
ComboFluxPlot
```

## Cumulative Sed Mass Plot (Figure 7)
```{r Figure 7 script, eval=TRUE, include=FALSE}
plot_vline <- read_csv('~/Documents/R Projects/Sed Traps/TO_Dates.csv') %>% 
  mutate(Date = as.Date(Date),
         Event = as.factor(Event),
         Reservoir = as.factor(Reservoir),
         Layer = 'Hypolimnion')

@@

```{r Figure 7, eval=TRUE, include=TRUE}
HypCumulFluxPlot
```

## Fe and Mn Threshold Plot (Figure 8)

```{r Fig 8 & 9 set up, eval=TRUE, include=FALSE}
metals <- metals_file %>% 
  filter(metals_file$DateTime >= as.Date('2018-01-01'),
         Site == 50, Reservoir == 'FCR' | Reservoir == 'BVR') %>% 
  select(Reservoir, Site, DateTime, Depth_m, TFe_mgL, SFe_mgL, TMn_mgL, SMn_mgL,
         Flag_TFe_mgL, Flag_TMn_mgL, Flag_SFe_mgL, Flag_SMn_mgL) %>%
  filter(Flag_TFe_mgL != 8 & Flag_SFe_mgL != 8 & Flag_TFe_mgL != 68 & Flag_SFe_mgL != 68,
         Flag_TMn_mgL != 8 & Flag_SMn_mgL != 8 & Flag_TMn_mgL != 68 & Flag_SMn_mgL != 68) %>% 
  mutate(FeDiff = TFe_mgL - SFe_mgL,
         MnDiff = TMn_mgL - SMn_mgL,
         STFe = SFe_mgL/TFe_mgL,
         STMn = SMn_mgL/TMn_mgL,
         Date = date(DateTime),
         Layer = NA,
         Layer = ifelse(Reservoir == 'FCR' & Depth_m <= 4, 'Epilimnion', Layer),
         Layer = ifelse(Reservoir == 'FCR' & Depth_m >= 4, 'Hypolimnion', Layer),
         Layer = ifelse(Reservoir == 'BVR' & Depth_m <= 5, 'Epilimnion', Layer),
         Layer = ifelse(Reservoir == 'BVR' & Depth_m >= 5, 'Hypolimnion', Layer),
         Year = year(DateTime)) %>% 
  group_by(Reservoir, Site, Date, Layer) %>% 
  mutate(AvgSTFe = mean(STFe, na.rm = TRUE),
         AvgSTMn = mean(STMn, na.rm = TRUE)) %>% 
  filter(FeDiff >= -0.02,
         MnDiff >= -0.06)

metals2023 <- metals %>% 
  filter(Year == 2023,
         MnDiff > 0)

@@

```{r Figure 8 script, eval=TRUE, include=FALSE}
#first find threshold dates, threshold = 0.3 mg/L for TMn and 0.9 mg/L for TFe

FeMnConcLeadingAvg <- metals %>% 
  filter(Reservoir == 'FCR' & Depth_m == 9) %>% 
  group_by(Reservoir, Depth_m, Year) %>%
  summarise(FeThresh = (lead(TFe_mgL, n = 2, order_by = Date) +
              lead(TFe_mgL, n = 1, order_by = Date) + TFe_mgL)/3,
            MnThresh = (lead(TMn_mgL, n = 2, order_by = Date) + 
              lead(TMn_mgL, n = 1, order_by = Date) + TMn_mgL)/3,
            Date = Date) %>% 
  ungroup() %>% 
  pivot_longer(cols = 4:5, values_to = 'Value', names_to = 'Thresh') %>%
  filter(Thresh == 'FeThresh' & Value >= 0.9 | Thresh == 'MnThresh' & Value >= 0.3) %>%
  group_by(Year, Thresh) %>%
  slice_min(order_by = Date) %>% 
  ungroup() %>%
  pivot_wider(names_from = Thresh, values_from = Date) %>%
  group_by(Reservoir, Depth_m, Year) %>% 
  summarise(MnThresh = mean(MnThresh, na.rm = TRUE),
            FeThresh = mean(FeThresh, na.rm = TRUE)) %>% 
  arrange(Year)

StratStart <- read_csv('StratStart2018_2023.csv') %>% 
  select(-c(length, end, method)) %>% 
  rename('Year' = 'year', 'StratStart' = 'start', 'Reservoir' = 'site_id')

#First HOx activation dates, where HOx was activated for more than 7 days before deactivation, see Table 1 in manuscript
HOxOn <- HOxBoxes %>%
  mutate(Duration = HOxOff - HOxOn) %>% 
  filter(Duration >= 7) %>% 
  select(Reservoir, Year, HOxOn) %>% 
  group_by(Reservoir, Year) %>% 
  slice_min(order_by = HOxOn)

FeMnThresh <- FeMnConcLeadingAvg %>% 
  full_join(StratStart) %>% 
  full_join(HOxOn) %>% 
  mutate(StratHOxDiff = as.numeric(HOxOn - StratStart),
         DaysToMnThresh = as.numeric(MnThresh - StratStart),
         DaysToFeThresh = as.numeric(FeThresh - StratStart))

MnThreshPlot <- ggplot(FeMnThresh) +
  theme_bw(base_size = 18) + 
  scale_y_continuous(limits = c(-15,100)) +
  scale_x_continuous(limits = c(-20,120), breaks = c(-20, 0, 20, 40, 60, 80, 100, 120)) +
  geom_vline(xintercept = 0, linewidth = 0.2) + geom_hline(yintercept = 0, linewidth = 0.2) +
  geom_point(aes(StratHOxDiff, DaysToMnThresh, color = as.factor(Year), shape = as.factor(Year)), size = 5) +
  guides(color = guide_legend(title = 'Year'), shape = guide_legend(title = 'Year')) +
  xlab('Time of HOx Activation Relative to Stratification (days)') + ylab('Manganese')

FeThreshPlot <- ggplot(FeMnThresh) +
  theme_bw(base_size = 18) + 
  scale_y_continuous(limits = c(-15,100)) +
  scale_x_continuous(limits = c(-20,120), breaks = c(-20, 0, 20, 40, 60, 80, 100, 120)) + xlab(NULL) +
  geom_vline(xintercept = 0, linewidth = 0.2) + geom_hline(yintercept = 0, linewidth = 0.2) +
  geom_point(aes(StratHOxDiff, DaysToFeThresh, color = as.factor(Year), shape = as.factor(Year)), size = 5) +
  guides(color = guide_legend(title = 'Year'), shape = guide_legend(title = 'Year')) + 
  xlab('') + ylab('Iron')

ThreshPlot <- ggarrange(FeThreshPlot, MnThreshPlot, ncol = 1, common.legend = TRUE, legend = 'bottom')
ThreshPlotFinal <- annotate_figure(ThreshPlot, left = text_grob('Time to Exceed Water Quality Threshold (days)', rot = 90, size = 18, hjust = 0.4))
```

```{r Figure 8, eval=TRUE, include=TRUE}
plot(ThreshPlotFinal)
```

## 2023 and 2020 Comparison of 9m TFe, SFe, TMn, SMn in FCR (Figure 9)

```{r Fig 9 script, eval=TRUE, include=FALSE}
Fe23 <- metals2023 %>% 
  select(Reservoir, Date, Site, Layer, Year, Depth_m, TFe_mgL, SFe_mgL, TO) %>%
  rename('Total' = 'TFe_mgL', 'Soluble' = 'SFe_mgL') %>% 
  pivot_longer(cols = 7:8, names_to = 'Type', values_to = 'Fe_mgL') %>% 
  filter(Layer == 'Hypolimnion')

@@

## Flux Plot (Figure S1)

@@

## DO plot (Figure S3)

@@

DO1 <- FCRDO %>%
  mutate(DateTime = as.POSIXct(DateTime, format = "%Y-%m-%d %H:%M:%S")) %>% 
  select(Reservoir, Site, DateTime, RDO_mgL_9_adjusted) %>% 
  mutate(Date = date(DateTime)) %>% 
  group_by(Reservoir, Site, Date) %>% 
  summarise(DO_mgL_9m = mean(RDO_mgL_9_adjusted, na.rm = TRUE)) %>% 
  mutate(across(c('DO_mgL_9m'), ~ifelse(is.nan(.), NA, .)),
         Year = year(Date)) %>% 
  pivot_longer(cols = 4, names_to = 'Depth_m', values_to = 'DO_mgL') %>%
  mutate(Depth_m = factor(Depth_m, levels = c('DO_mgL_9m'),
                          labels = c('9'))) %>% 
  drop_na()

DO2 <- BVRDO1 %>% 
  select(Reservoir, Site, DateTime, RDO_mgL_13) %>% 
  mutate(Date = date(DateTime)) %>% 
  group_by(Reservoir, Site, Date) %>% 
  summarise(DO_mgL_13m = mean(RDO_mgL_13, na.rm = TRUE)) %>% 
  mutate(across(c('DO_mgL_13m'), ~ifelse(is.nan(.), NA, .)),
         Year = year(Date)) %>% 
  pivot_longer(cols = 4, names_to = 'Depth_m', values_to = 'DO_mgL') %>%
  mutate(Depth_m = factor(Depth_m, levels = c('DO_mgL_13m'),
                          labels = c('13'))) %>% 
  drop_na()

DO3 <- BVRDO2 %>% 
  filter(DateTime >= as.Date('2018-01-01')) %>% 
  select(Reservoir, Site, DateTime, MiniDotDO_mgL_10) %>% 
  mutate(Date = date(DateTime)) %>% 
  group_by(Reservoir, Site, Date) %>% 
  summarise(DO_mgL_10m = mean(MiniDotDO_mgL_10, na.rm = TRUE)) %>% 
  mutate(across(c('DO_mgL_10m'), ~ifelse(is.nan(.), NA, .)),
         Year = year(Date)) %>% 
  pivot_longer(cols = 4, names_to = 'Depth_m', values_to = 'DO_mgL') %>%
  mutate(Depth_m = factor(Depth_m, levels = c('DO_mgL_10m'),
                          labels = c('10')))

DO <- DO1 %>% 
  full_join(DO2) %>% 
  full_join(DO3) %>% 
  filter(Date <= as.Date('2023-12-31')) %>% 
  arrange(Date)

DO_plot1 <- DO %>% 
  ggplot() +
  scale_x_date(name = '', date_breaks = '1 year', date_labels = '%Y') +
  theme_bw(base_size = 18) + theme(panel.grid = element_blank()) +
  geom_path(aes(x = Date, y = DO_mgL, color = Reservoir)) + 
  ylab('Dissolved Oxygen (mg/L)')
```

@@

## DO on HOx Activation Day Plot (Figure S4)
```{r DO plot figure S4 script, eval=TRUE, include=FALSE}
DOps1 <- FCRDO %>%
  select(Reservoir, Site, DateTime, RDOsat_percent_9_adjusted) %>% 
  mutate(Date = date(DateTime)) %>%
  group_by(Reservoir, Site, Date) %>% 
  summarise(AvgDOsat_percent_9 = mean(RDOsat_percent_9_adjusted, na.rm = TRUE)) %>% 
  ungroup() %>% #now select first HOx activation dates
  filter(Date == as.Date('2018-04-23') | Date == as.Date('2019-06-03') | 
           Date == as.Date('2020-06-29') | Date == as.Date('2021-06-11') |
           Date == as.Date('2022-05-19') | Date == as.Date('2023-03-06')) %>% 
  mutate(Year = year(Date))

DO_CumulMetalMass <- CumulFluxSummary %>%
  ungroup() %>% 
  filter(Reservoir == 'FCR',
         Year >= 2019) %>% 
  select(Reservoir, Year, FeFlux, MnFlux) %>% 
  full_join(DOps1)

>>>>

## Data sources:

1. Schreiber, M.E., C.E. Wood, A. Breef-Pilz, C.E. Bauer, G. Haynie, R. Keverline, M. Kricheldorf, and E. Tipper. 2024. Time series of total and soluble metal concentrations from Falling Creek Reservoir, Beaverdam Reservoir, and Carvins Cove Reservoir in southwestern Virginia, USA from 2014 through 2023 ver 8. Environmental Data Initiative. https://doi.org/10.6073/pasta/584b1daf7f1541bc595aa3a9dd71a2c7.

2. Schreiber, M.E., C.E. Wood, C.E. Bauer, A. Breef-Pilz, G.K. Haynie, and E.M. Tipper. 2024. Sediment trap time series data for Beaverdam Reservoir and Falling Creek Reservoir in southwestern Virginia, USA 2018 through 2023 ver 8. Environmental Data Initiative. https://doi.org/10.6073/pasta/5ee061465e62c29587042c58e7a91e13.

3. Carey, C.C., A. Breef-Pilz, V. Daneshmand, A.D. Delany, and R.Q. Thomas. 2024. Time series of high-frequency sensor data measuring water temperature, dissolved oxygen, pressure, conductivity, specific conductance, total dissolved solids, chlorophyll a, phycocyanin, fluorescent dissolved organic matter, and turbidity at discrete depths in Falling Creek Reservoir, Virginia, USA in 2018-2023 ver 8. Environmental Data Initiative. https://doi.org/10.6073/pasta/7541e8d297850be7c613d116156735a9.

4. Carey, C.C. and A. Breef-Pilz. 2025. Time series of high-frequency sensor data measuring water temperature, dissolved oxygen, conductivity, specific conductance, total dissolved solids, chlorophyll a, phycocyanin, fluorescent dissolved organic matter, and turbidity at discrete depths, and water level in Beaverdam Reservoir, Virginia, USA in 2009-2024 ver 5. Environmental Data Initiative. https://doi.org/10.6073/pasta/8f666b34c120aa5d2242964cf3147f90.

5. Carey, C.C., A. Breef-Pilz, H.L. Wander, D.W. Howard, G.K. Haynie, M.K. Kricheldorf, S. Tannheiser, and E.M. Tipper. 2025. Secchi depth data and discrete depth profiles of water temperature, dissolved oxygen, conductivity, specific conductance, photosynthetic active radiation, oxidation-reduction potential, and pH for Beaverdam Reservoir, Carvins Cove Reservoir, Falling Creek Reservoir, Gatewood Reservoir, and Spring Hollow Reservoir in southwestern Virginia, USA 2013-2024 ver 13. Environmental Data Initiative. https://doi.org/10.6073/pasta/0df2b12c947e52a8d0240a75d20bbc1e.

## Figures 6-9, S1, S3, and S4
```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(pacman)
pacman::p_load(tidyverse, readxl, stringr, readr, glmnet, ISLR, lubridate, ggplot2, ggpubr, stats, gridExtra, graphics, gt)
```

@@

BVRDO2 <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/725/5/b7f0524aee78dcf4a2452a203a39c1f2")

Handhelds  <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/198/13/e50a50d062ee73f4d85e4f20b360ce4f")
```

```{r set up file path}
#set up file path for figures, change if necessary
myFilePath <- './figures'
```

## Figure 6. DO at HOx Activation vs Max Fe and Mn concentrations

```{r DO plot figure 6 script, eval=TRUE, include=FALSE}

#First HOx activation dates, where HOx was activated for more than 7 days before deactivation, see Table 1 in manuscript

HOxOn <- HOxBoxes %>%
  mutate(Duration = HOxOff - HOxOn) %>% 
  filter(Duration >= 7) %>% 
  select(Reservoir, Year, HOxOn) %>% 
  group_by(Reservoir, Year) %>% 
  slice_min(order_by = HOxOn)

DOps1 <- FCRDO %>%
  select(Reservoir, Site, DateTime, RDOsat_percent_9_adjusted) %>% 
  mutate(Date = date(DateTime)) %>%
  group_by(Reservoir, Site, Date) %>% 
  summarise(AvgDOsat_percent_9 = mean(RDOsat_percent_9_adjusted, na.rm = TRUE)) %>% 
  ungroup() %>% #now select first HOx activation dates
  filter(Date == as.Date('2018-04-23') | Date == as.Date('2019-06-03') | 
           Date == as.Date('2020-06-29') | Date == as.Date('2021-06-11') |
           Date == as.Date('2022-05-19') | Date == as.Date('2023-03-06')) %>% 
  mutate(Year = year(Date)) %>% 
  rename('HOxStart' = 'Date')

DO_Handhelds <- Handhelds %>% 
  filter(Reservoir == 'FCR') %>% 
  mutate(Date = date(DateTime),
         Year = year(DateTime)) %>% #HOx activated on 2018-04-23 @ noon
  filter(DateTime == as_datetime('2018-04-23 09:45:00') & Depth_m == 9) %>% 
  select(Reservoir, Site, Date, Year, DOsat_percent) %>% 
  rename('HOxStart' = 'Date',
         'AvgDOsat_percent_9' = 'DOsat_percent')

DOps2 <- DOps1 %>% 
  full_join(DO_Handhelds)

metals <- metals_file %>% 
  filter(metals_file$DateTime >= as.Date('2018-01-01'),
         Site == 50, Reservoir == 'FCR' | Reservoir == 'BVR') %>% 
  select(Reservoir, Site, DateTime, Depth_m, TFe_mgL, SFe_mgL, TMn_mgL, SMn_mgL,
         Flag_TFe_mgL, Flag_TMn_mgL, Flag_SFe_mgL, Flag_SMn_mgL) %>%
  filter(Flag_TFe_mgL != 8 & Flag_SFe_mgL != 8 & Flag_TFe_mgL != 68 & Flag_SFe_mgL != 68,
         Flag_TMn_mgL != 8 & Flag_SMn_mgL != 8 & Flag_TMn_mgL != 68 & Flag_SMn_mgL != 68) %>% 
  mutate(FeDiff = TFe_mgL - SFe_mgL,
         MnDiff = TMn_mgL - SMn_mgL,
         STFe = SFe_mgL/TFe_mgL,
         STMn = SMn_mgL/TMn_mgL,
         Date = date(DateTime),
         Layer = NA,
         Layer = ifelse(Reservoir == 'FCR' & Depth_m <= 4, 'Epilimnion', Layer),
         Layer = ifelse(Reservoir == 'FCR' & Depth_m >= 4, 'Hypolimnion', Layer),
         Layer = ifelse(Reservoir == 'BVR' & Depth_m <= 5, 'Epilimnion', Layer),
         Layer = ifelse(Reservoir == 'BVR' & Depth_m >= 5, 'Hypolimnion', Layer),
         Year = year(DateTime)) %>% 
  group_by(Reservoir, Site, Date, Layer) %>% 
  mutate(AvgSTFe = mean(STFe, na.rm = TRUE),
         AvgSTMn = mean(STMn, na.rm = TRUE)) %>% 
  filter(FeDiff >= -0.02,
         MnDiff >= -0.06)

MaxMetals <- metals %>% 
  filter(Year >= 2018 & Depth_m == 9 & Reservoir == 'FCR') %>% 
  filter(Year == 2018 & between(Date, as.Date('2018-04-23'), as.Date('2018-08-12')) | #only include dates where HOx
           Year == 2019 & between(Date, as.Date('2019-06-03'), as.Date('2019-11-20'))  | #was active
           Year == 2020 & between(Date, as.Date('2020-06-29'), as.Date('2020-12-02')) |
           Year == 2021 & between(Date, as.Date('2021-06-11'), as.Date('2021-12-06')) |
           Year == 2022 & between(Date, as.Date('2022-05-19'), as.Date('2022-12-12')) |
           Year == 2023 & between(Date, as.Date('2023-03-06'), as.Date('2023-12-04'))) %>% 
  group_by(Reservoir, Site, Year) %>% 
  summarise(MaxTFe_mgL = max(TFe_mgL),
            MaxTMn_mgL = max(TMn_mgL))

DO_MaxMetalMass <- DOps2 %>% 
  full_join(MaxMetals)

DO_MaxMetal_Feplot <- DO_MaxMetalMass %>% 
  ggplot() + theme_bw(base_size = 18) +
  geom_point(aes(x = AvgDOsat_percent_9, y = MaxTFe_mgL, color = as.factor(Year),
                 shape = as.factor(Year)), size = 3) +
  ylab('Maximum Concentration (mg/L)') + xlab('') +
  guides(color = guide_legend(title = 'Year'), shape = guide_legend(title = 'Year')) +
  ggtitle('Total Iron')

DO_MaxMetal_Mnplot <- DO_MaxMetalMass %>% 
  ggplot() + theme_bw(base_size = 18) +
  geom_point(aes(x = AvgDOsat_percent_9, y = MaxTMn_mgL, color = as.factor(Year),
                 shape = as.factor(Year)), size = 3) +
  ylab('') + xlab('') +
  guides(color = guide_legend(title = 'Year'), shape = guide_legend(title = 'Year')) +
  ggtitle('Total Manganese')

DO_MaxMetal_plot <- ggarrange(DO_MaxMetal_Feplot, DO_MaxMetal_Mnplot, nrow = 1, common.legend = TRUE,
                              legend = 'right', labels = c('A', 'B'))
DO_MaxMetal_plotFinal <- annotate_figure(DO_MaxMetal_plot, bottom = text_grob('Dissolved Oxygen at HOx Activation (% saturation)', size = 18, hjust = 0.53, vjust = -1))
```

```{r Figure 6, eval=TRUE, include=TRUE}
DO_MaxMetal_plotFinal
```

## Figure 7. Seasonal Flux Paired T-Test Plot

```{r Fig 7 and 8 set up, eval=TRUE, include=FALSE}
 fluxes2018_2023 <-  fluxes %>% 
  select(Reservoir, Date, Depth_m, Duration_days, TFeFlux_gm2d, TMnFlux_gm2d) %>% 
  na.omit() %>%
  mutate(Layer = if_else(Depth_m <= 5, 'Epilimnion', 'Hypolimnion'),
         Year = year(Date))

@@

```{r Figure 7 script, eval=TRUE, include=FALSE}
CumulFePlot1 <- CumulFluxSummary %>% 
  ggplot() + theme_bw(base_size = 18) + ggtitle('Iron') + ylab('Fe Flux (g/m2d)') +
  geom_point(aes(x = Reservoir, y = FeFlux, color = as.factor(Year), shape = as.factor(Year)), size = 3) +
  #2018
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.209, yend = 1.196, alpha = 0.5,
               color = "#F8766D", linetype = 3) +
  #2019
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.661, yend = 1.398, alpha = 0.5,
               color = "#B79F00", linetype = 3) +
  #2020
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.276, yend = 1.676, alpha = 0.5,
               color = "#00BA38", linetype = 3) +
  #2021
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.775, yend = 1.776, alpha = 0.5,
               color = "#00BFC4", linetype = 3) +
  #2022
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.867, yend = 1.849, alpha = 0.5,
               color = "#619CFF", linetype = 3) +
  #2023
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.819, yend = 1.017, alpha = 0.5,
               color = "#F564E3", linetype = 3) +
  annotate(geom = 'text', x= 1.5, y = 1.8, label = '**', size = 12) +
  guides(color = guide_legend(title = 'Year'), shape = guide_legend(title = 'Year'))

@@

```{r Figure 7, eval=TRUE, include=TRUE}
ComboFluxPlot
```

## Figure 8. Cumulative Sed Mass Plot
```{r Figure 8 script, eval=TRUE, include=FALSE}
plot_vline <- read_csv('~/Documents/R Projects/Sed Traps/TO_Dates.csv') %>% 
  mutate(Date = as.Date(Date),
         Event = as.factor(Event),
         Reservoir = as.factor(Reservoir),
         Layer = 'Hypolimnion')

@@

```{r Figure 8, eval=TRUE, include=TRUE}
HypCumulFluxPlot
```

## Figure 9. 2023 and 2020 Comparison of 9m TFe, SFe, TMn, SMn in FCR

```{r Figure 9 set up, eval=TRUE, include=FALSE}
metals2023 <- metals %>% 
  filter(Year == 2023,
         MnDiff > 0)

@@

```{r Figure 9 script, eval=TRUE, include=FALSE}
Fe23 <- metals2023 %>% 
  select(Reservoir, Date, Site, Layer, Year, Depth_m, TFe_mgL, SFe_mgL, TO) %>%
  rename('Total' = 'TFe_mgL', 'Soluble' = 'SFe_mgL') %>% 
  pivot_longer(cols = 7:8, names_to = 'Type', values_to = 'Fe_mgL') %>% 
  filter(Layer == 'Hypolimnion')

@@

## Figure S1. Flux Plot

@@

## Figure S3. DO plot

@@

DO1 <- FCRDO %>%
  mutate(DateTime = as.POSIXct(DateTime, format = "%Y-%m-%d %H:%M:%S")) %>% 
  select(Reservoir, Site, DateTime, RDO_mgL_9_adjusted) %>% 
  mutate(Date = date(DateTime)) %>% 
  group_by(Reservoir, Site, Date) %>% 
  summarise(DO_mgL_9m = mean(RDO_mgL_9_adjusted, na.rm = TRUE)) %>% 
  mutate(across(c('DO_mgL_9m'), ~ifelse(is.nan(.), NA, .)),
         Year = year(Date)) %>% 
  pivot_longer(cols = 4, names_to = 'Depth_m', values_to = 'DO_mgL') %>%
  mutate(Depth_m = factor(Depth_m, levels = c('DO_mgL_9m'),
                          labels = c('9')),
         Method = 'edi.271.9') %>% 
  drop_na()

DO2 <- BVRDO1 %>% 
  select(Reservoir, Site, DateTime, RDO_mgL_13) %>% 
  mutate(Date = date(DateTime)) %>% 
  group_by(Reservoir, Site, Date) %>% 
  summarise(DO_mgL_13m = mean(RDO_mgL_13, na.rm = TRUE)) %>% 
  mutate(across(c('DO_mgL_13m'), ~ifelse(is.nan(.), NA, .)),
         Year = year(Date)) %>% 
  pivot_longer(cols = 4, names_to = 'Depth_m', values_to = 'DO_mgL') %>%
  mutate(Depth_m = factor(Depth_m, levels = c('DO_mgL_13m'),
                          labels = c('13')),
         Method = 'edi.725.5') %>% 
  drop_na()

DO3 <- BVRDO2 %>% 
  filter(DateTime >= as.Date('2018-01-01')) %>% 
  select(Reservoir, Site, DateTime, MiniDotDO_mgL_10) %>% 
  mutate(Date = date(DateTime)) %>% 
  group_by(Reservoir, Site, Date) %>% 
  summarise(DO_mgL_10m = mean(MiniDotDO_mgL_10, na.rm = TRUE)) %>% 
  mutate(across(c('DO_mgL_10m'), ~ifelse(is.nan(.), NA, .)),
         Year = year(Date)) %>% 
  pivot_longer(cols = 4, names_to = 'Depth_m', values_to = 'DO_mgL') %>%
  mutate(Depth_m = factor(Depth_m, levels = c('DO_mgL_10m'),
                          labels = c('10')),
         Method = 'edi.725.5') %>% 
  drop_na()

DO4 <- Handhelds %>% 
  mutate(Date = date(DateTime),
         Year = year(DateTime)) %>% #HOx activated on 2018-04-23 @ noon
  filter(Year == 2018| Year == 2019 | Year == 2020,
         Reservoir == 'BVR' & Depth_m == 10 & 
           between(Date, as.Date('2018-05-04'), as.Date('2018-12-05'))|
           Reservoir == 'BVR' & Depth_m == 10 & 
           between(Date, as.Date('2019-05-18'), as.Date('2020-03-14'))|
           Reservoir == 'BVR' & Depth_m == 10 & 
           between(Date, as.Date('2020-05-16'), as.Date('2020-06-17'))|
           Reservoir == 'FCR' & Depth_m == 9 & Date < as.Date('2018-08-19')) %>% 
  select(Reservoir, Site, Date, Year, Depth_m, DO_mgL) %>% 
  mutate(Depth_m = factor(Depth_m),
         Method = 'edi.198.13') %>% 
  drop_na()

DO <- DO1 %>% 
  full_join(DO2) %>% 
  full_join(DO3) %>%
  full_join(DO4) %>% 
  filter(Date <= as.Date('2023-12-31')) %>%
  mutate(Method = factor(Method, levels = c('edi.271.9', 'edi.725.5', 'edi.198.13'))) %>%
  ungroup() %>% 
  #add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2018-11-17'),
  #        Year = 2018, Depth_m = as.factor(10), DO_mgL = NA, 
  #        Method = as.factor('edi.198.13')) %>%
  add_row(Reservoir = 'FCR', Site = 50, Date = as.Date('2018-08-19'),
          Year = 2018, Depth_m = as.factor(9), DO_mgL = NA, 
          Method = as.factor('edi.198.13')) %>%
  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2018-12-05'),
          Year = 2018, Depth_m = as.factor(10), DO_mgL = NA, 
          Method = as.factor('edi.198.13')) %>%
  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2019-05-17'),
          Year = 2019, Depth_m = as.factor(10), DO_mgL = NA, 
          Method = as.factor('edi.198.13')) %>%
  #add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2019-10-18'),
  #        Year = 2019, Depth_m = as.factor(10), DO_mgL = NA, 
  #        Method = as.factor('edi.198.13')) %>%
  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2020-01-01'),
          Year = 2020, Depth_m = as.factor(10), DO_mgL = NA, 
          Method = as.factor('edi.725.5')) %>% 
  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2020-03-15'),
          Year = 2020, Depth_m = as.factor(10), DO_mgL = NA, 
          Method = as.factor('edi.198.13')) %>% 
    add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2020-05-15'),
          Year = 2020, Depth_m = as.factor(10), DO_mgL = NA, 
          Method = as.factor('edi.198.13')) %>%
  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2020-06-05'),
          Year = 2020, Depth_m = as.factor(10), DO_mgL = NA, 
          Method = as.factor('edi.198.13')) %>%
arrange(Date)

DO_plot1 <- DO %>% 
  ggplot() +
  scale_x_date(name = '', date_breaks = '1 year', date_labels = '%Y') +
  theme_bw(base_size = 18) + theme(panel.grid = element_blank()) +
  geom_line(aes(x = Date, y = DO_mgL, color = Reservoir, linetype = Method)) +
  scale_linetype_manual(values = c('solid', 'solid', 'dotted')) + 
  guides(linetype = guide_legend(title = 'Data Package')) +
  ylab('Dissolved Oxygen (mg/L)')
```

@@

## Figure S4. DO on HOx Activation Day Plot
```{r DO plot figure S4 script, eval=TRUE, include=FALSE}

HOxOnCumulFluxes2018_2023 <- avgFluxes2018_2023 %>% 
  filter(TO == 'Pre' & Layer == 'Hypolimnion') %>%
  filter(Year == 2018 & between(Date, as.Date('2018-04-23'), as.Date('2018-08-12')) | #only include dates where HOx
           Year == 2019 & between(Date, as.Date('2019-06-03'), as.Date('2019-11-20'))  | #was active
           Year == 2020 & between(Date, as.Date('2020-06-29'), as.Date('2020-12-02')) |
           Year == 2021 & between(Date, as.Date('2021-06-11'), as.Date('2021-12-06')) |
           Year == 2022 & between(Date, as.Date('2022-05-19'), as.Date('2022-12-12')) |
           Year == 2023 & between(Date, as.Date('2023-03-06'), as.Date('2023-12-04'))) %>% 
  group_by(Reservoir, Layer, Year) %>% 
  mutate(CumulFe_gm2 = cumsum(AvgTFeFlux_gm2d*Duration_days),
         CumulMn_gm2 = cumsum(AvgTMnFlux_gm2d*Duration_days),
         CumulDuration_days = cumsum(Duration_days))

HOxOnCumulFluxSummary <- HOxOnCumulFluxes2018_2023 %>%
  group_by(Reservoir, Layer, Year) %>% 
  summarise(CumulFe_gm2 = max(CumulFe_gm2),
            CumulMn_gm2 = max(CumulMn_gm2),
            Duration_days = sum(Duration_days),
            Date = max(Date)) %>% 
  mutate(FeFlux = round(CumulFe_gm2/Duration_days, digits = 3),
         MnFlux = round(CumulMn_gm2/Duration_days, digits = 3))

DO_CumulMetalMass <- HOxOnCumulFluxSummary %>%
  ungroup() %>% 
  filter(Reservoir == 'FCR',
         Year >= 2018) %>% 
  select(Reservoir, Year, FeFlux, MnFlux) %>% 
  full_join(DOps2)
